---
title: "Motor Development Survey Analysis"
author: "Shari Liu"
date: "11/11/2018"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(comment = "##")
options(scipen = 0, digits = 3)

## load required packages
ipak <- function (pkg) {
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}


packages <- c("tidyverse", "lme4", "lmerTest", "stringr", "cowplot", "effects", "PropCIs", "mice")

ipak(packages)

```

<!-- # Simulating and making dataset -->
<!-- ## Simulating Dataset -->

<!-- ```{r motorDataSim} -->
<!-- n <- 20 # sample size -->
<!-- sd <- 0.75 # standard deviation -->
<!-- subj <- c(1:n) # subjects -->


<!-- # here, each variable is the month at which an infant started performing an action. for each variable, we sample from a normal distribution centered around a mean. we also make certain values depend on each other. -->
<!-- simData <- as.data.frame(subj) %>% -->
<!--   mutate( -->
<!--     reaches = rnorm(n, 5, sd), -->
<!--     rolls = reaches + rnorm(n, 0, sd), -->
<!--     sits = rolls + rnorm(n, 1, sd), -->
<!--     crawls = sits + rnorm(n, 2, sd), -->
<!--     handtohand = reaches + rnorm(n, 2, sd), -->
<!--     pullstand = crawls + rnorm(n, 4, sd), -->
<!--     pincer = handtohand + rnorm(n, 1, sd), -->
<!--     hiddensearch = rnorm(n, 8, sd), -->
<!--     stands = rnorm(n, 11, sd), -->
<!--     cruises = stands + rnorm(n, 1, sd), -->
<!--     fearheights = crawls + rnorm(n, 3, sd), -->
<!--     walks = cruises + rnorm(n, 2, sd), -->
<!--     strangerdanger = rnorm(n, 9, sd), -->
<!--     waves = rnorm(n, 10, sd), -->
<!--     points = waves + rnorm(n, .5, sd), -->
<!--     expectation = rnorm(n, .6, .2) # proportion looking to unexpected -->
<!--   ) -->

<!-- # categories of behaviors -->
<!-- objectdirected <- c("reaches", "handtohand", "pincer", "hiddensearch") -->
<!-- action <- c("rolls", "sits", "crawls", "pullstand", "stands", "cruises",  "walks", "fearheights") -->
<!-- social <- c("strangerdanger", "waves", "points") -->
<!-- socialcognition <- c("expectation") -->

<!-- simLong <- simData %>% gather(iv, dv, -subj) %>% -->
<!--   mutate(category = case_when(iv %in% objectdirected ~ "objectdirected", -->
<!--                               iv %in% action ~ "action", -->
<!--                               iv %in% social ~ "social", -->
<!--                               iv %in% socialcognition ~ "socialcognition")) -->


<!-- # to save this dataset to a csv (and analyzed with spss) -->
<!-- write.csv(simData, "simData.csv") -->

<!-- ``` -->

<!-- ```{r plots} -->

<!-- # age in months of all actions, grouped by category -->
<!-- plot1 <- ggplot(data = filter(simLong, iv != "expectation"), aes(reorder(iv, dv), dv, fill = category)) -->
<!-- plot1 + geom_boxplot() + -->
<!--   geom_point(alpha = 0.5) +  -->
<!--   coord_flip() + -->
<!--   theme_bw(20) + -->
<!--   xlab("Action")+ -->
<!--   ylab("Age in Months")+ -->
<!--   theme(legend.position="top") -->


<!-- corr <- correlate(simData) -->
<!-- corr2 <- focus(corr, -subj, -expectation, mirror = TRUE) -->

<!-- # correlation plot -->
<!-- rplot(corr2, print_cor = TRUE) -->
<!-- ``` -->

<!-- ## Make combined dataset -->



<!-- ```{r} -->
<!-- setwd('/Users/shariliu/Documents/HarvardLDS/Studies/RISK/github/inferring_value_from_risk/analyses/') -->
<!-- lt <- read.csv('risk_data.csv', header = TRUE) -->
<!-- motor <- read.csv('action_data.csv', header = TRUE) %>%  rename(experiment = Study, rn=RN, subj_orig = subject_ID) -->

<!-- risk_lt <- lt %>% filter(experiment=="RISK10" | experiment=="RISK13") -->
<!-- mr_lt <- lt %>% filter(experiment=="MR10" | experiment == "MR13") -->

<!-- mr_motor <- motor %>% filter(experiment=="MR") -->
<!-- risk_motor <- motor %>% filter(experiment=="RISK" | experiment=="RISKr") -->

<!-- mr_combined <- full_join(mr_lt, mr_motor, by="rn") -->
<!-- risk_combined <- full_join(risk_lt, risk_motor, by="subj_orig") -->

<!-- combined <- bind_rows(mr_combined, risk_combined) -->
<!-- write.csv(combined, "motordata_combined.csv") -->
<!-- ``` -->



# Working with empirical dataset
Across two experiments, we found that by 13 months of age, infants are sensitive to the perils of other people's actions. We tested this in the context of cliffs of varying depth -- the deeper the cliff, the more dangerous the action. We tested both 10 and 13mo infants in these experiments, and found robust evidence for sensitivity to danger in 13mo, and more mixed evidence at 10mo. One key question is why: Why do 13mo succeed more robustly than 10mo? This report explores one potential cause of this finding, which is that 13mo have more experience navigating through the world themselves, and thus have more first-person experience with potentially dangerous situations (e.g. cruising along walls, pulling themselves up to stand, etc). 

This report asks 2 questions:

(1) Are there differences in the motor competencies of 10 and 13mo in these experiments?

(2) If yes, do these differences predict differences in performance on their analysis of other agents' perils?


## Descriptives

```{r loaddata}

setwd("~/Documents/HarvardLDS/Studies/RISK/github/analyses")

original <- read.csv("motordata_combined.csv")

str(original)

action_ages_full <- original %>% 
  select(-ends_with("y.n")) %>% 
  gather(action,age, reaches:walks) %>%
  mutate(age = as.numeric(as.character(age))) %>%
  spread(action,age) %>%
  select(X, crawls:waves) 

action_ages <- as.data.frame(action_ages_full) %>%
  rename(subj = X) %>%
  as.data.frame()

# categories of behaviors
objectdirected <- c("reaches", "handtohand", "pincer", "hiddensearch")
selflocomotion <- c("rolls", "sits", "crawls", "pullstand", "stands", "cruises",  "walks")
anxiety <- c("strangerdanger", "fearheights")
social <- c("waves", "points")


data <- original %>% select(-ends_with("y.n")) %>% 
  # mutate(diff = avg.higher - avg.lower) %>%
  gather(action,age, reaches:walks) %>%
  mutate(age = as.numeric(as.character(age))) %>%
  spread(action,age) %>%
  select(X, experiment.x, agem, age.at.survey, prop.lower, prop.higher, avg.lower, avg.higher, crawls:waves) %>%
  mutate(X = as.factor(X)) %>%
  rename(subj=X, age.at.study=agem) %>%
  mutate(exp = as.factor(case_when(experiment.x == "MR13" | experiment.x=="MR10" ~ "MR",
                         experiment.x == "RISK10" | experiment.x=="RISK13" ~ "RISK"))) %>%
  mutate(agegroup = as.factor(case_when(age.at.study<12 ~ "10", age.at.study>12 ~ "13")))%>%
  mutate(looking.to.unexp = case_when (exp == "MR" ~ prop.higher,
                                       exp == "RISK" ~ prop.lower)) %>%
  mutate(LTdiff = case_when(exp == "MR" ~ avg.higher-avg.lower,
                            exp == "RISK" ~ avg.lower-avg.higher)) %>%
  gather(action,age,crawls:waves) %>%
  mutate(category = as.factor(case_when(action %in% objectdirected ~ "objectdirected",
                              action %in% selflocomotion ~ "selflocomotion",
                              action %in% anxiety ~ "anxiety",
                              action %in% social ~ "social"))) %>%
  mutate(monthsPerformed = age.at.study-age)


data.yn <- original %>% select(X, experiment.x, ends_with("y.n")) %>%
  gather(action, yesno, reaches_y.n:walks_y.n) %>%
  mutate(yesno = tolower(yesno)) %>%
  mutate(action = str_remove(action, "_y.n")) %>%
  mutate(X = as.factor(X)) %>%
  rename(subj=X) 

full_data <- full_join(data.yn, data) %>%
    mutate(yesnoAtStudy = case_when(age.at.survey-age.at.study<.25 & yesno=="yes" ~ 1,
                                    age.at.survey-age.at.study<.25 & yesno=="no" ~ 0,
                                    age > age.at.study ~ 0,
                                    age <= age.at.study ~ 1))

```

```{r}

no_data <- full_data %>% filter(is.na(yesnoAtStudy) & is.na(age)) %>%
  group_by(subj) %>% summarize(n=n()) %>% 
  filter(n==15) %>%
  select(subj)
```

```{r impute.means}
`%notin%` <- function(x,y) !(x %in% y)

# full_data_filtered <- full_data %>%
#   filter(subj %notin% no_data$subj) 
# 
# data.wide.imputed <- mice(data.wide,m=1,maxit=1,meth='mean',seed=50)
# 
# complete(data.wide.imputed)

# write.csv(complete(data.wide.imputed), file = "motordata_imputed.csv")

data.wide.imputed <- read.csv("motordata_imputed.csv")

```


```{r load.imputed.data}

full_data_imputed <- read.csv("motordata_imputed.csv")

data_imputed_long <- full_data_imputed %>%
  # mutate(diff = avg.higher - avg.lower) %>%
  gather(action,age, reaches:walks) %>%
  mutate(age = as.numeric(as.character(age))) %>%
  mutate(exp = as.factor(case_when(experiment.x == "MR13" | experiment.x=="MR10" ~ "MR",
                         experiment.x == "RISK10" | experiment.x=="RISK13" ~ "RISK"))) %>%
  mutate(agegroup = as.factor(case_when(age.at.study<12 ~ "10", age.at.study>12 ~ "13")))%>%
  mutate(looking.to.unexp = case_when (exp == "MR" ~ prop.higher,
                                       exp == "RISK" ~ prop.lower)) %>%
  mutate(LTdiff = case_when(exp == "MR" ~ avg.higher-avg.lower,
                            exp == "RISK" ~ avg.lower-avg.higher)) %>%
  gather(action,age,crawls:waves) %>%
  mutate(category = as.factor(case_when(action %in% objectdirected ~ "objectdirected",
                              action %in% selflocomotion ~ "selflocomotion",
                              action %in% anxiety ~ "anxiety",
                              action %in% social ~ "social"))) %>%
  mutate(monthsPerformed = age.at.study-age)

data_imputed_long$subj <- as.factor(data_imputed_long$subj)

combined_data_imputed <- full_join(data.yn, data_imputed_long) %>%
    mutate(yesnoAtStudy = case_when(age.at.survey-age.at.study<.25 & yesno=="yes" ~ 1,
                                    age.at.survey-age.at.study<.25 & yesno=="no" ~ 0,
                                    age > age.at.study ~ 0,
                                    age <= age.at.study ~ 1))
```


## Question 1: Are there differences in motor competence at 10 and 13mo?

First, let's just see when infants begin reliably doing things. 

```{r ages}
# age in months of all actions, grouped by category
full_data$action <- as.factor(full_data$action)
ggplot(data = full_data %>% na.omit(), aes(x=reorder(action,age), y=age, fill=category)) +
  geom_boxplot()+
  geom_jitter(width=.2, height=0.2)+
  stat_summary(fun.y=mean, geom="point", colour="white", size=3)+
  scale_y_continuous(breaks=seq(0,20,2))+
  coord_flip() +
  # theme_bw(20) +
  xlab("Action")+
  ylab("Age in Months")+
  theme(legend.position="bottom")

```


Here's a plot of how many months of experience kids have with each action, relative to the day they participated in the study. Unsurprisingly, 13mo have a lot more experience with all actions. 

```{r daysperformed}
data %>%
  na.omit() %>%
  ggplot(aes(reorder(action,monthsPerformed),monthsPerformed, fill=category)) +
  # ggplot(aes(agegroup,monthsPerformed, fill=category)) +
  geom_jitter(width=0, height=0.1, size=1)+
  stat_summary(fun.y="mean", geom="bar", colour="black")+
  stat_summary(fun.data=mean_cl_boot, geom="errorbar", colour="red", width=0.1, size=1)+
  # coord_flip()+
  scale_y_continuous(breaks=seq(-12,12,2))+
  xlab("Action")+
  ylab("Months of Experience with Action Relative to Study")+
  facet_wrap(~agegroup)+
  # facet_wrap(~action)+
  theme(legend.position="bottom", axis.text.x = element_text(angle = 45, hjust = 1))
```

Next, we can look at differences in the proportion of 13mo and 10mo participants across all our actions. If the 95% CIs do not overlap (e.g. for 10mo an estimate is .3-.5 and for 13mo .55-.8), then we can say that there are reliable differences across these two groups on that action.

```{r proportionmakedata}
prop_data <- full_data %>%
  na.omit() %>%
  group_by(category,action, agegroup,yesnoAtStudy) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  mutate(total = sum(n)) %>%
  as.data.frame()
  
for (i in 1:nrow(prop_data)){
  prop_data$lower[i] <- exactci(prop_data$n[i], prop_data$total[i], conf.level=0.95)$conf.int[1]
  prop_data$upper[i] <- exactci(prop_data$n[i], prop_data$total[i], conf.level=0.95)$conf.int[2]
}

prop_data %>%
  filter(yesnoAtStudy==1)
```

Another way to do this is to look at the plot below. It looks like cruising, hiddensearch, points, pullstand, stands, walks, and waves are the actions that differ between the two age groups.

```{r proportionplot}
prop_data %>%
  filter(yesnoAtStudy==1) %>%
  # ggplot(aes(reorder(action,freq),freq, fill=category)) +
  ggplot(aes(agegroup,freq, fill=category)) +
  geom_bar(stat="identity", colour="black")+
  geom_errorbar(aes(ymin=lower, ymax=upper), width=0.1, size=1)+
  xlab("Age Group")+
  ylab("Proportion of Infants Who Perform Action")+
  # facet_wrap(~agegroup)+
  facet_wrap(~action)+
  theme(legend.position="bottom", axis.text.x=element_text(angle=45,hjust=1))
```

Here's the same plot organized by age group, instead of action.

```{r proportiondata}
prop_data %>%
  filter(yesnoAtStudy==1) %>%
  ggplot(aes(reorder(action,freq),freq, fill=category)) +
  # ggplot(aes(agegroup,freq, fill=category)) +
  geom_bar(stat="identity", colour="black")+
  geom_errorbar(aes(ymin=lower, ymax=upper), width=0.1, size=1)+
  xlab("Action")+
  ylab("Proportion of Infants Who Perform Action")+
  facet_wrap(~agegroup)+
  # facet_wrap(~action)+
  theme(legend.position="bottom", axis.text.x=element_text(angle=45,hjust=1))
```


## Question 2: Do differences in motor competence predict infants' performance?

Ok, so there definitely are differences in the motor competencies across the two age groups in our study. The next question is whether these differences actually predict infants' looking times. 

Here's a plot looking at infants' looking times, organized by whether they do or don't reliably perform a given action at the time of their participation in the looking time study. 

```{r plotpred}

full_data %>% 
  na.omit() %>%
ggplot(aes(reorder(as.factor(yesnoAtStudy),looking.to.unexp),looking.to.unexp, fill=category))+
  geom_boxplot()+
  geom_jitter(width=.1, height=0.2)+
  stat_summary(fun.y=mean, geom="point", colour="red", size=3)+
  stat_summary(fun.data="mean_cl_boot", geom="errorbar", colour="red", width=0.1, size=1)+
  facet_wrap(~action,nrow=2)+
  geom_hline(yintercept = .50) + 
  scale_y_continuous(breaks=seq(0,1,.1))+
  xlab("Infant Performs Action at Time of Study")+
  ylab("Proportion LT to Unexpected")+
  theme(legend.position="bottom")
```


Here's a plot relating how many months of experience kids have with a given action and their looking times.

```{r}
full_data %>% 
  na.omit() %>%
  ggplot(aes(monthsPerformed, looking.to.unexp, colour=category))+
  geom_hline(yintercept = .50) + 
  geom_point(alpha=0.2)+
  geom_smooth(method="lm")+
  facet_wrap(~action)
```


Ok, so far, we don't see much signal. But the best way to investigate this is to simultaneously regress these experience-based predictors on looking times. 

First, we're going to look at whether infants do an action or not at the time of the study, and ask whether doing or not doing an action predicts infants' proportion looking to the unexpected event. This analysis controls of kids' age. 

```{r yesno, fig.height=12}
# set contrasts for analysis - compare effects against the grand mean
op <- options(contrasts = c("contr.sum", "contr.poly"))

LT_data_yesno <- full_data %>% 
  select(subj, agegroup, age.at.study, exp, action, yesnoAtStudy, looking.to.unexp, LTdiff) %>%
  mutate(yesnoAtStudy = as.factor(yesnoAtStudy)) %>%
  spread(action, yesnoAtStudy)

LT_data_yesno_MR <- LT_data_yesno %>% 
  filter(exp == "MR")

LT_data_yesno_RISK <- LT_data_yesno %>% 
  filter(exp == "RISK")

model1 <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves + age.at.study, data=LT_data_yesno_MR)
summary(model1)
# plot(allEffects(model))
# 
model2 <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves + age.at.study, data=LT_data_yesno_RISK)
summary(model2)
# plot(allEffects(model2))

model3 <- lm(looking.to.unexp ~ crawls + cruises + fearheights + handtohand + hiddensearch + pincer + points + pullstand + stands + strangerdanger + walks +  waves + age.at.study, data=LT_data_yesno)
summary(model3)
plot(allEffects(model3))
```

Here's the same analysis with imputed values for missing data, generated using the `mice()` function using the weighted predictive mean matching (the `midastouch` method).

```{r}
# set contrasts for analysis - compare effects against the grand mean
op <- options(contrasts = c("contr.sum", "contr.poly"))

LT_data_yesno_imp <- full_data_imputed %>% 
  select(subj, agegroup, age.at.study, exp, action, yesnoAtStudy, looking.to.unexp, LTdiff) %>%
  mutate(yesnoAtStudy = as.factor(yesnoAtStudy)) %>%
  spread(action, yesnoAtStudy)

LT_data_yesno_MR_imp <- LT_data_yesno_imp %>% 
  filter(exp == "MR")

LT_data_yesno_RISK_imp <- LT_data_yesno_imp %>% 
  filter(exp == "RISK")

model1.imp <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves + age.at.study, data=LT_data_yesno_MR_imp)
summary(model1.imp)
# plot(allEffects(model))
# 
model2.imp <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves + age.at.study, data=LT_data_yesno_RISK_imp)
summary(model2.imp)
# plot(allEffects(model2))

model3.imp <- lm(looking.to.unexp ~ crawls + cruises + fearheights + handtohand + hiddensearch + pincer + points + pullstand + stands + strangerdanger + walks +  waves + age.at.study, data=LT_data_yesno_imp)
summary(model3.imp)
plot(allEffects(model3.imp))
```


Next, we do the same analysis except that we're going to use the continuous predictors of the number of months' experience kids have with different actions. This analysis controls for kids' age. 

```{r daysexp, fig.height=12}
LT_data_months <- full_data %>% 
  select(subj, agegroup, age.at.study, exp, action, monthsPerformed, looking.to.unexp, LTdiff) %>%
  # mutate(yesnoAtStudy = as.factor(yesnoAtStudy)) %>%
  spread(action, monthsPerformed)

LT_data_months_MR <- LT_data_months %>% 
  filter(exp=="MR")

LT_data_months_RISK <- LT_data_months %>% 
  filter(exp=="RISK")

model3 <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves, data=LT_data_months_MR)
summary(model3)
# plot(allEffects(model3))
# 
model4 <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves, data=LT_data_months_RISK)
summary(model4)
# plot(allEffects(model4))

model5 <- lm(looking.to.unexp ~ crawls + cruises + fearheights + handtohand + hiddensearch + pincer + points + pullstand + stands + strangerdanger + walks + waves + age.at.study, data=LT_data_months, na.action=na.exclude)
summary(model5)
plot(allEffects(model5))

```

Here's the same analysis with imputed values for missing data, generated using the `mice()` function using the weighted predictive mean matching (the `midastouch` method).

```{r daysexp_imp, fig.height=12}

LT_data_month_imp <- full_data_imputed 
  # select(subj, agegroup, age.at.study, exp, action, monthsPerformed, looking.to.unexp, LTdiff) 
  # mutate(yesnoAtStudy = as.factor(yesnoAtStudy)) %>%
  # spread(action, monthsPerformed)

LT_data_months_MR_imp <- LT_data_month_imp %>% 
  filter(exp=="MR")

LT_data_months_RISK_imp <- LT_data_month_imp %>% 
  filter(exp=="RISK")

model3.imp <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves, data=LT_data_months_MR_imp)
summary(model3.imp)
# plot(allEffects(model3))
# 
model4.imp <- lm(looking.to.unexp ~ cruises + points + pullstand + stands + walks + waves, data=LT_data_months_RISK_imp)
summary(model4.imp)
# plot(allEffects(model4))

model5.imp <- lm(looking.to.unexp ~ crawls + cruises + fearheights + handtohand + hiddensearch + pincer + points + pullstand + stands + strangerdanger + walks + waves + age.at.study, data=LT_data_month_imp, na.action=na.exclude)
summary(model5.imp)
plot(allEffects(model5.imp))

```

# Datasets

1. Only complete cases (LT + motor).
2. Only complete cases, MR.
3. Only complete cases, RISK.
4. Full data (with imputed means) (LT + motor).
5. Full data (with imputed means), MR.
6. Full data (with imputed means), RISK.