---
title: "Dangerous ground: Thirteen-month-old infants are sensitive to peril in other people’s actions "
author: "Shari Liu"
date: "April 19 2019"
output:
  html_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(comment = "##", echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE, include=TRUE, dependson="risk.wide")
options(scipen = 0, digits = 3)

## load required packages
ipak <- function (pkg) {
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

# devtools::install_github("mhtess/rwebppl")

packages <- c("tidyverse", "Hmisc", "lattice", "multcomp", "lsmeans", "schoRsch", "influence.ME", "lme4", "effects", "lmerTest", "cowplot", "irr", "simr", "bayestestR")

ipak(packages)

```

```{r prep.data}

# read in data
wide <- read.csv(file = "risk_data.csv", header = TRUE)
head(wide)
str(wide)

# convert into long format
long <- gather(wide, type, look, avg.lower:pre.high)
str(long)

# log transform looks
long$look <- as.numeric(long$look)
long$loglook <- log(long$look)

# set levels for different kinds of looks
long$type <- factor(long$type)
levels(long$type) <- c("Higher", "Lower", "Higher 1", "Higher 2",
                           "Lower 1", "Lower 2", "Prefam High", "Prefam Low", "Binary Pref", "Prop Higher", "Prop Lower")

# subset averaged looks across test pairs (2 observations per participant)
long.avg <- long %>% 
  filter(type == "Lower" | type == "Higher") %>%
  mutate(agegroup = as.factor(case_when(agem < 12 ~ "10 months",
                            agem > 12 ~ "13 months")))

long.avg$type <- factor(long.avg$type)

# subset looks for 2 test pairs (4 observations per participant)
long.tp <- dplyr::filter(long, type == "Higher 1" | type == "Higher 2" |
                          type == "Lower 1" | type == "Lower 2")%>%
  mutate(agegroup = as.factor(case_when(agem < 12 ~ "10 months",
                            agem > 12 ~ "13 months")))

# subset looks during control videos in Exp 1 and 3
mr.pre <- long %>% filter(type=="Prefam High" | type=="Prefam Low") %>% 
    mutate(agegroup = as.factor(case_when(agem < 12 ~ "10 months",
                            agem > 12 ~ "13 months"))) %>%
  drop_na()


# organize type and test pairs
long.tp$tp <- NA
long.tp$type <- factor(long.tp$type)
long.tp$trial <- NA
for (i in 1:nrow(long.tp)) {
  if (long.tp$type[i] == "Lower 1") {
    long.tp$tp[i] <- "First"
  }
  if (long.tp$type[i] == "Higher 1") {
    long.tp$tp[i] <- "First"
  }
  if (long.tp$type[i] == "Lower 2") {
    long.tp$tp[i] <- "Second"
  }
  if (long.tp$type[i] == "Higher 2") {
    long.tp$tp[i] <- "Second"
  }
  if ((long.tp$type[i] == "Lower 1" & long.tp$first_test[i] == "LV") | (long.tp$type[i] == "Higher 1" & long.tp$first_test[i] == "HV")) {
    long.tp$trial[i] <- "1"
  }
  if ((long.tp$type[i] == "Lower Value 2" & long.tp$first_test[i] == "LV")  | (long.tp$type[i] == "Higher Value 2" & long.tp$first_test[i] == "HV")) {
    long.tp$trial[i] <- "3"
  }
  if ((long.tp$type[i] == "Higher Value 1" & long.tp$first_test[i] == "LV")  | (long.tp$type[i] == "Lower Value 1" & long.tp$first_test[i] == "HV")) {
    long.tp$trial[i] <- "2"
  }
  if ((long.tp$type[i] == "Higher Value 2" & long.tp$first_test[i] == "LV")  | (long.tp$type[i] == "Lower Value 2" & long.tp$first_test[i] == "HV")) {
    long.tp$trial[i] <- "4"
  }
}

long.tp$tp <- factor(long.tp$tp)
long.tp$type <- factor(long.tp$type)
levels(long.tp$type) <- c("Higher Value", "Higher Value", "Lower Value", "Lower Value")
long.tp$trial <- factor(long.tp$trial)

# set baseline levels for analysis:
long.avg$type <- relevel(long.avg$type, ref = "Lower")
mr.pre$type <- relevel(mr.pre$type, ref = "Prefam Low")

long.avg$exp <- relevel(long.avg$exp, ref = "Exp.1")
long.avg$sex <- relevel(long.avg$sex, ref = "m")

exp1.avg <-dplyr::filter(long.avg, exp == "Exp.1")
exp2.avg <-dplyr::filter(long.avg, exp == "Exp.2")
exp3.avg <-dplyr::filter(long.avg, exp == "Exp.3")
luts.exp3 <- dplyr::filter(long.avg, experiment == "LUTS.Exp.3")

risk.avg <- long.avg %>%
  filter(cost == "Risk") %>%
  mutate(task = as.factor(case_when((experiment == "RISK10" | experiment == "RISK13") ~ "infer.value",
                          (experiment == "MR10" | experiment == "MR13") ~ "min.risk"))) 
risk.avg$type <- relevel(risk.avg$type, "Lower")
mr.pre$type <- relevel(mr.pre$type, ref = "Prefam Low")

op <- options(contrasts = c("contr.treatment", "contr.poly")) # treatment contrasts
```

```{r prep.functions}
# function for identifying influential observations, and then returning a new model without them
# INPUTS: model = model name, data = dataset, and subj = column heading for observations
# OUTPUT: model excluding influential subjects
exclude.cooks <- function(model, data, subj) {
  cooks <- cooks.distance(influence(model, subj))
  cutoff <- 4/length(unique(data$subj))
  new.model <- exclude.influence(model, grouping = subj, level=data[which(cooks > cutoff),]$subj)
  return(new.model)
}

# function that computes CIs and returns them in df
gen.ci <- function(model) {
  df <- data.frame(confint(model))
  names(df) <- c("lower", "upper")
  return(df)
}

# function that converts model summary to df
gen.m <- function(model) {
  df <- data.frame(coef(summary(model)))
  names(df) <- c("est", "se", "df", "t", "p")
  return(df)
}

# function that returns age info and number of females in a dataset, assuming 2 rows of data per subj
info <- function(longdata) {
  longdata %>% summarize(mean = mean(agem), min=range(agem)[1], max=range(agem)[2], f=sum(sex=="f")/2, n=length(unique(subj)))
}

## Retrieved from : http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#error-bars-for-within-subjects-variables
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=TRUE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- plyr::rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}
## Norms the data within specified groups in a data frame; it normalizes each
## subject (identified by idvar) so that they have the same mean, within each group
## specified by betweenvars.
##   data: a data frame.
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   na.rm: a boolean that indicates whether to ignore NA's
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=TRUE, .drop=TRUE) {
  library(plyr)
  
  # Measure var on left, idvar + between vars on right of formula.
  data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
                         .fun = function(xx, col, na.rm) {
                           c(subjMean = mean(xx[,col], na.rm=na.rm))
                         },
                         measurevar,
                         na.rm
  )
  
  # Put the subject means with original data
  data <- merge(data, data.subjMean)
  
  # Get the normalized data in a new column
  measureNormedVar <- paste(measurevar, "_norm", sep="")
  data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
    mean(data[,measurevar], na.rm=na.rm)
  
  # Remove this subject mean column
  data$subjMean <- NULL
  
  return(data)
}

## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=TRUE, conf.interval=.95, .drop=TRUE) {
  
  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
                       FUN=is.factor, FUN.VALUE=logical(1))
  
  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }
  
  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)
  
  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL
  
  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)
  
  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")
  
  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)
  
  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                                  FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )
  
  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor
  
  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}


# function that returns column of standardized betas from lmer model
gen.beta <- function(model) {
  f <- data.frame(fixef(model))
  colnames(f) <- "beta"
  return(f)
}

# function that computes CIs and returns them in df
gen.ci <- function(model) {
  df <- data.frame(confint(model))
  names(df) <- c("lower", "upper")
  return(df)
}

# function that converts model summary (lmer) to df
gen.m <- function(model) {
  df <- data.frame(coef(summary(model)))
  names(df) <- c("est", "se", "df", "t", "p")
  return(df)
}

# function that converts model summary (lm) to df
gen.lm <- function(model) {
  df <- data.frame(coef(summary(model)))
  names(df) <- c("est", "se", "t", "p")
  return(df)
}

# function that returns APA-formatted result from lme4/lmerTest table
report <- function(table, index, places, tails) {
  if (tails == "1") {
    p <- round(table$p[index], places)/2
    howmanytails <- "one-tailed"
  } else {
    p <- round(table$p[index], places)
    howmanytails <- "two-tailed"
  }
  if (p < .001) {
    p <- "<.001"
  } else {
    p <- paste("=", round(p,places), sep = "")
  }
  result <- paste("[", round(table$lower[index], places), ",", round(table$upper[index], places), "], ß=", round(table$beta[index], places), ", B=", round(table$est[index],places), ", SE=", round(table$se[index],places), ", p", p, ", ", howmanytails, sep = "")
  return(result)
}

```

```{r summary}
## get within-subjects CIs for plotting
summary.avg <- summarySEwithin(data = risk.avg, measurevar = "look", betweenvars = c("exp","agegroup"), withinvars = "type", idvar = "subj")

summary.1013 <- summarySEwithin(data = risk.avg, measurevar = "look", betweenvars = c("task"), withinvars = "type", idvar = "subj")

summary.pre <- summarySEwithin(data = mr.pre, measurevar = "look", betweenvars = c("exp","agegroup"), withinvars = "type", idvar = "subj")

summary.pre.1013 <- summarySEwithin(data = mr.pre, measurevar = "look",  withinvars = "type", idvar = "subj")


```

```{r ntrialsexcluded}
nexclude <- long.tp %>%
  filter(cost == "Risk") %>%
  group_by(exp) %>%
  summarise_all(funs(sum(is.na(.))))
```

## Reliability
```{r reliability}

rel <- read.csv(file = "risk_reliability.csv", header=TRUE)
exp1 <- rel %>% filter(experiment.new=="Exp.1")
exp2 <- rel %>% filter(experiment.new=="Exp.2")
exp3 <- rel %>% filter(experiment.new=="Exp.3")

exp1rel <- icc(data.frame(exp1$secondary.look, exp1$orig.look),model="one", type="agreement")

exp2rel <- icc(data.frame(exp2$secondary.look, exp2$orig.look),model="one", type="agreement")

exp3rel <- icc(data.frame(exp3$secondary.look, exp3$orig.look),model="one", type="agreement")

```

# Figures

```{r fig.exp12, include=TRUE, fig.width=16}
risk.avg$type<- relevel(risk.avg$type, "Higher")
risk1 <- ggplot(data = risk.avg %>% filter(task == "infer.value"), aes(type, look, fill = type))+
    facet_grid(~exp+agegroup)+
  geom_boxplot(outlier.colour = NA, alpha = 0.8)+
  stat_summary(fun.y = mean, alpha = 0.8, geom = "point", shape=21, size=3, position = "dodge", colour = "red", fill = "red") +
  ylab("Looking Time (s)") +
  xlab("Test Event") +
  geom_errorbar(data = summary.avg %>% filter(exp=="Exp.2" | exp =="Exp.1"), colour="red", position = position_dodge(width = 5), width = 0, aes(ymin=look-ci, ymax=look+ci)) +
  # geom_point(data = summary.avg %>% filter(experiment=="RISK10" | experiment =="RISK13"), colour="red",position = position_dodge(width = 0), aes(y=look))+
  coord_cartesian(ylim = c(0, 65)) +
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.2, aes(group = subj))+
  scale_x_discrete(labels = c("Higher Peril Goal\n(Higher Value)", "Lower Peril Goal\n(Lower Value)"))+
  # theme_linedraw(15)+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Greys")+
  annotate("text", colour="red", x=1.5, y=63, size=5, label=c("*ß=0.354", "ß=0.168")) +
  scale_colour_brewer(palette="Greys")+
  background_grid(major = "xy", minor = "xy")


risk2 <- ggplot(data = risk.avg %>% filter(task == "infer.value"), aes(type, look, fill = type))+
  geom_boxplot(outlier.colour = NA, alpha = 0.8)+
  stat_summary(fun.y = mean, alpha = 0.8, geom = "point", shape=21, size=3, position = "dodge", colour = "red", fill = "red") +
  ylab("Looking Time (s)") +
  xlab("Test Event") +
  coord_cartesian(ylim = c(0, 65)) +
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.2, aes(group = subj))+
  # facet_grid(~agegroup)+
  geom_errorbar(data = summary.1013 %>% filter(task=="infer.value"), colour="red", position = position_dodge(width = 5), width = 0, aes(ymin=look-ci, ymax=look+ci)) +
  # geom_point(data = summary.avg, aes(type, look))+
  scale_x_discrete(labels = c("Higher Peril Goal\n(Higher Value)", "Lower Peril Goal\n(Lower Value)"))+
  annotate("text", colour="red", x=1.5, y=63, size=5, label=c("*ß=0.265")) +
  # theme_linedraw(15)+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Greys")+
  scale_colour_brewer(palette="Greys")+
  background_grid(major = "xy", minor = "xy")

plot_grid(risk1, risk2, labels = c("A", "B"), nrow=1, rel_widths=c(2,1.2))
```

**Figure 3.** Looking time towards the test events presenting approaches to the goals attained through actions of higher vs. lower peril in Experiments 1-2, both (A) within and (B) collapsed across experiments.  Red error bars around means indicate within-subjects 95% confidence intervals. Pairs of points indicate data from a single participant. Horizontal bars within boxes indicate medians, and boxes indicate the middle 2 quartiles of data.  Beta coefficients (ß) indicate effect sizes in standard deviations.

```{r fig.exp3, include=TRUE, fig.width=16, fig.height=16}
mr1 <- ggplot(data = risk.avg %>% filter(exp == "Exp.3"), aes(type, look, fill = type)) +
  geom_boxplot(outlier.colour = NA, alpha = 0.8)+
  stat_summary(fun.y = mean, alpha = 0.8, geom = "point", shape=21, size=3, position = "dodge", colour = "red", fill = "red") +
  ylab("Looking Time (s)") +
  xlab("Test Event") +
  coord_cartesian(ylim = c(0, 65)) +
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.2, aes(group = subj))+
  facet_grid(~exp+agegroup)+
  geom_errorbar(data = summary.avg %>% filter(exp == "Exp.3"), colour="red", position = position_dodge(width = 5), width = 0, aes(ymin=look-ci, ymax=look+ci)) +
  # geom_point(data = summary.avg, aes(type, look))+
  scale_x_discrete(labels = c("Less Perilous\n(Shallower Trench)","More Perilous\n(Deeper Trench)"))+
  annotate("text", colour="red", x=1.5, y=63, size=5, label=c("*ß=0.386", "*ß=0.356")) +
  # theme_linedraw(15)+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Greys")+
  scale_colour_brewer(palette="Greys")+
  background_grid(major = "xy", minor = "xy")

mr2 <- ggplot(data = risk.avg %>% filter(exp == "Exp.3"), aes(type, look, fill = type)) +
  geom_boxplot(outlier.colour = NA, alpha = 0.8)+
  stat_summary(fun.y = mean, alpha = 0.8, geom = "point", shape=21, size=3, position = "dodge", colour = "red", fill = "red") +
  ylab("Looking Time (s)") +
  xlab("Test Event") +
  coord_cartesian(ylim = c(0, 65)) +
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.2, aes(group = subj))+
  # facet_grid(~agegroup)+
  geom_errorbar(data = summary.1013 %>% filter(task=="min.risk"), colour="red", position = position_dodge(width = 5), width = 0, aes(ymin=look-ci, ymax=look+ci)) +
  # geom_point(data = summary.avg, aes(type, look))+
  scale_x_discrete(labels = c("Less Perilous\n(Shallower Trench)","More Perilous\n(Deeper Trench)"))+
  annotate("text", colour="red", x=1.5, y=63, size=5, label=c("***ß=0.410")) +
  # theme_linedraw(15)+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Greys")+
  scale_colour_brewer(palette="Greys")+
  background_grid(major = "xy", minor = "xy")

mr3 <- ggplot(data = mr.pre, aes(type, look, fill = type))+
  geom_boxplot(outlier.colour = NA, alpha = 0.8)+
  stat_summary(fun.y = mean, alpha = 0.8, geom = "point", shape=21, size=3, position = "dodge", colour = "red", fill = "red") +
  ylab("Looking Time (s)") +
  xlab("Control Event") +
  coord_cartesian(ylim = c(0, 65)) +
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.2, aes(group = subj))+
  facet_grid(~exp+agegroup)+
  # stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour="red", position = position_dodge(width = 5), width = 0) +
  geom_errorbar(data = summary.pre, colour="red", position = position_dodge(width = 5), width = 0, aes(ymin=look-ci, ymax=look+ci), alpha = 0.8) +
  scale_x_discrete(labels = c("Shallower Trench", "Deeper Trench"))+
  annotate("text", colour="red", x=1.5, y=63, size=5, label=c("ß=-0.109", "**ß=-0.339")) +
  # theme_linedraw(15)+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Greys")+
  scale_colour_brewer(palette="Greys")+
  background_grid(major = "xy", minor = "xy")

mr4 <- ggplot(data = mr.pre, aes(type, look, fill = type))+
  geom_boxplot(outlier.colour = NA, alpha = 0.8)+
  stat_summary(fun.y = mean, alpha = 0.8, geom = "point", shape=21, size=3, position = "dodge", colour = "red", fill = "red") +
  ylab("Looking Time (s)") +
  xlab("Control Event") +
  coord_cartesian(ylim = c(0, 65)) +
  geom_point(alpha = 0.1)+
  geom_line(alpha = 0.2, aes(group = subj))+
  # facet_grid(~exp)+
  # stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour="red", position = position_dodge(width = 5), width = 0) +
  geom_errorbar(data = summary.pre.1013, colour="red", position = position_dodge(width = 5), width = 0, aes(ymin=look-ci, ymax=look+ci), alpha = 0.8) +
  scale_x_discrete(labels = c("Shallower Trench","Deeper Trench"))+
  annotate("text", colour="red", x=1.5, y=63, size=5, label=c("*ß=-0.277")) +
  # theme_linedraw(15)+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Greys")+
  scale_colour_brewer(palette="Greys")+
  background_grid(major = "xy", minor = "xy")

plot_grid(mr1, mr2, mr3, mr4, labels = c("A", "B", "C", "D"), rel_widths = c(1.8,1,1.8,1))

```

**Figure 4.**  Looking times from Experiment during the test events, in which the agent chose to jump across a deeper or shallower trench for a goal (A and B), and during the control events, in which infants’ attention was drawn over the deeper and shallower trenches (C and D). The looking times are presented by separately (A and C) and collapsed across age groups (B and D). Red error bars around means indicate within-subjects 95% confidence intervals. Pairs of points indicate data from a single participant. Horizontal bars within boxes indicate medians, and boxes indicate the middle 2 quartiles of data. Beta coefficients (ß) list effect sizes in standard deviations.

# Experiment 1: Inferring value from risk (13-month-old infants)

```{r exp1.primary}
exp1.avg$type <- relevel(exp1.avg$type, ref = "Higher")


exp1.0 <- lmer(loglook ~ 1 + (1|subj),
               data = exp1.avg)

exp1.1 <- lmer(loglook ~ type + (1|subj),
               data = exp1.avg)

# id influential observations
plot(influence(exp1.1, "subj"), which="cook",
     cutoff=4/32, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp1.1.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp1.avg %>% filter(subj != "S4_13"))

exp1.1.table <- gen.m(exp1.1.cooks)
exp1.1.ci <- gen.ci(exp1.1.cooks)[3:4,]

exp1.1.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = exp1.avg %>% filter(subj != "S4_13"))
exp1.1.betas <- gen.beta(exp1.1.beta)

exp1.results <- cbind(exp1.1.table, exp1.1.betas,exp1.1.ci)


```

# Experiment 2: Inferring value from risk (10-month-old infants)

```{r exp2.primary}
exp2.0 <- lmer(loglook ~ 1 + (1|subj),
               data = exp2.avg)

exp2.1 <- lmer(loglook ~ type + (1|subj),
               data = exp2.avg)

# id influential observations
plot(influence(exp2.1, "subj"), which="cook",
     cutoff=4/32, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation, exclude

exp2.1.cooks <- lmer(loglook ~ type + (1|subj),
               data = filter(exp2.avg, subj != "S5_25"))

exp2.1.table <- gen.m(exp2.1.cooks)
exp2.1.ci <- gen.ci(exp2.1.cooks)[3:4,]

exp2.1.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = filter(exp2.avg, subj != "S5_25"))
exp2.1.betas <- gen.beta(exp2.1.beta)

exp2.results <- cbind(exp2.1.table, exp2.1.betas,exp2.1.ci)
```

# Experiments 1 and 2: Inferring value from risk (10 and 13-month-old infants)

```{r exp12.diff}

exp12.avg <- long.avg %>% 
  filter(exp == "Exp.1" | exp == "Exp.2") %>% 
  mutate(agegroup = as.factor(case_when(agem < 12 ~ "10 months",
                            agem > 12 ~ "13 months")))

exp12.avg$type <- relevel(exp12.avg$type, ref = "Higher")

exp12.1 <- lmer(loglook ~ type * agegroup + (1|subj),
               data = exp12.avg)

# id influential observations
plot(influence(exp12.1, "subj"), which="cook",
     cutoff=4/64, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation, exclude

exp12.1.cooks <- lmer(loglook ~ type * agegroup + (1|subj),
               data = exp12.avg %>% filter(subj != "S5_25"))

exp12.1.table <- gen.m(exp12.1.cooks)
exp12.1.ci <- gen.ci(exp12.1.cooks)[3:4,]

exp12.1.beta <- lmer(scale(loglook) ~ type * agegroup  + (1|subj),
               data = exp12.avg %>% filter(subj != "S5_25"))
exp12.1.betas <- gen.beta(exp12.1.beta)

exp12.results <- cbind(exp12.1.table, exp12.1.betas,exp12.1.ci)
```

```{r exp12.collapsing}

exp12.2 <- lmer(loglook ~ type + (1|subj) + (1|exp),
               data = exp12.avg)

# id influential observations
plot(influence(exp12.2, "subj"), which="cook",
     cutoff=4/64, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation, exclude

exp12.2.cooks <- lmer(loglook ~ type + (1|subj) + (1|exp),
               data = exp12.avg %>% filter(subj != "S5_25"))

exp12.2.table <- gen.m(exp12.2.cooks)
exp12.2.ci <- gen.ci(exp12.2.cooks)[4:5,]

exp12.2.beta <- lmer(scale(loglook) ~ type  + (1|subj) + (1|exp),
               data = exp12.avg %>% filter(subj != "S5_25"))
exp12.2.betas <- gen.beta(exp12.2.beta)

exp12.results2 <- cbind(exp12.2.table, exp12.2.betas,exp12.2.ci)
```

# Comparing Exp 2 and LUTS Exp 3
```{r exp2.luts.diff}

exp2.luts.avg <- long.avg %>% 
  filter(experiment == "RISK10" | experiment == "LUTS.Exp.3") 

exp2.luts.avg$type <- relevel(exp2.luts.avg$type, ref = "Higher")

exp2.luts.1 <- lmer(loglook ~ type * experiment + (1|subj),
               data = exp2.luts.avg)

# id influential observations
plot(influence(exp2.luts.1, "subj"), which="cook",
     cutoff=4/64, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation, exclude

exp2.luts.1.cooks <- lmer(loglook ~ type * experiment  + (1|subj),
               data = exp2.luts.avg %>% filter(subj != "S3_15"))

exp2.luts.1.table <- gen.m(exp2.luts.1.cooks)
exp2.luts.1.ci <- gen.ci(exp2.luts.1.cooks)[3:4,]

exp2.luts.1.beta <- lmer(scale(loglook) ~ type * experiment  + (1|subj),
               data = exp2.luts.avg %>% filter(subj != "S3_15"))
exp2.luts.1.betas <- gen.beta(exp2.luts.1.beta)

exp2.luts.results <- cbind(exp2.luts.1.table, exp2.luts.1.betas,exp2.luts.1.ci)
```

```{r exp2.luts.collapsing}

#### IMPT: Model fails to converge if experiment is also added as random intercept
exp2.luts.2 <- lmer(loglook ~ type + (1|subj),
               data = exp2.luts.avg)

# id influential observations
plot(influence(exp2.luts.2, "subj"), which="cook",
     cutoff=4/64, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation, exclude

exp2.luts.2.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp2.luts.avg %>% filter(subj != "S5_25"))

exp2.luts.2.table <- gen.m(exp2.luts.2.cooks)
exp2.luts.2.ci <- gen.ci(exp2.luts.2.cooks)[3:4,]

exp2.luts.2.beta <- lmer(scale(loglook) ~ type+ (1|subj),
               data = exp2.luts.avg %>% filter(subj != "S5_25"))
exp2.luts.2.betas <- gen.beta(exp2.luts.2.beta)

exp2.luts.results2 <- cbind(exp2.luts.2.table, exp2.luts.2.betas,exp2.luts.2.ci)
```

To ask whether 10-month-old infants responded differently in this experiment, wherein agents jumped over cliffs of varying depth, and a past experiment, wherein agents jumped over cliffs of varying width (Experiment 3, Liu et al., 2017), we compared their looking preferences at test across these 2 experiments. We found that infants did not respond significantly differently when reasoning about action cost and action danger across 2 studies of identical experimental design and highly similar stimuli, (`r report(exp2.luts.results, 3, 3, 2)`, excluding one influential participant). Collapsing across both experiments, infants looked longer when the agent chose the goal for which it performed less dangerous or less costly actions, `r report(exp2.luts.results2,2,3,2)`).


# Experiment 3: Minimizing Risk, 10mo infants
```{r exp3a.primary}

exp3a.avg <- exp3.avg %>% filter(agegroup==10)

exp3a.info <- info(exp3a.avg)


exp3a.0 <- lmer(loglook ~ 1 + (1|subj),
               data = exp3a.avg)

exp3a.1 <- lmer(loglook ~ type + (1|subj),
               data = exp3a.avg)

# id influential observations
plot(influence(exp3a.1, "subj"), which="cook",
     cutoff=4/30, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation

exp3a.1.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp3a.avg %>% filter(subj != "03-MR"))
exp3a.1.table <- gen.m(exp3a.1.cooks)
exp3a.1.ci <- gen.ci(exp3a.1.cooks)[3:4,]

exp3a.1.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = exp3a.avg %>% filter(subj != "03-MR"))
exp3a.1.betas <- gen.beta(exp3a.1.beta)

exp3a.results <- cbind(exp3a.1.table, exp3a.1.betas, exp3a.1.ci)
```

```{r exp3a.pre}
exp3a.pre <- mr.pre %>% filter(agegroup == 10)

exp3a.2 <- lmer(loglook ~ type + (1|subj),
               data = exp3a.pre)

# id influential observations
plot(influence(exp3a.2, "subj"), which="cook",
     cutoff=4/30, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation

exp3a.2.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp3a.pre %>% filter(subj != "21-MR"))

exp3a.2.table <- gen.m(exp3a.2.cooks)
exp3a.2.ci <- gen.ci(exp3a.2.cooks)[3:4,]

exp3a.2.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = exp3a.pre %>% filter(subj != "21-MR"))
exp3a.2.betas <- gen.beta(exp3a.2.beta)

exp3a.results2 <- cbind(exp3a.2.table, exp3a.2.betas, exp3a.2.ci)
```

```{r exp3a.pre.vs.test}
exp3a.prefam.test <- long %>%
  filter(type == "Prefam High" | type == "Prefam Low" | type == "Higher" | type == "Lower") %>%
filter(experiment == "MR10") %>%
  mutate(phase = as.factor(case_when((type == "Prefam High" | type == "Prefam Low") ~ "prefam",
                           (type == "Higher" | type == "Lower") ~ "test"))) %>%
  mutate(cliff = as.factor(case_when((type == "Prefam High" | type == "Higher") ~ "deeper",
                                     (type == "Prefam Low" | type == "Lower") ~ "shallower")))

summary.mr <- summarySEwithin(data = exp3a.prefam.test, measurevar = "look", withinvars = c("cliff", "type", "phase"), idvar="subj")
  
exp3a.prefam.test$type <- as.factor(exp3a.prefam.test$type)

exp3a.3 <- lmer(loglook ~ cliff * phase + (1|subj),
                     data = exp3a.prefam.test)

plot(influence(exp3a.3, "subj"), which="cook",
     cutoff=4/30, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3a.3.table <- gen.m(exp3a.3)
exp3a.3.ci <- gen.ci(exp3a.3)[3:6,]

exp3a.3.beta <- lmer(scale(loglook) ~ cliff * phase + (1|subj),
                     data = exp3a.prefam.test)
exp3a.3.betas <- gen.beta(exp3a.3.beta)

exp3a.results3 <- cbind(exp3a.3.table,exp3a.3.betas,exp3a.3.ci)
```

## Results
### Main results.
Infants looked longer at test when the agent, at test, chose the higher-risk action than when the agent chose the lower-risk action (Mhigher=`r summary.avg$look[1]`s, Mlower=`r summary.avg$look[2]`s, `r report(exp3a.results, 2, 3, 1)`, mixed effect model with fixed effect of test event and random intercepts for participant identity, excluding one influential participant on the basis of Cook’s Distance (Nieuwenhuis et al., 2012)). This finding is consistent with an expectation that the agent would choose to perform the less perilous action. 

### Exploratory results.
Further analyses tested for an alternative explanation for this looking preference: Did infants simply prefer to look at events occurring over the deeper cliff?  To address this possibility, we compared infants’ looking times during control events, where their attention was drawn to each cliff, using an attention-getting star that was placed in the path of the agent’s subsequent actions. We found that overall, infants no strong preference in this context (Mdeep=`r summary.pre$look[1]`s, Mshallow=`r summary.pre$look[2]`s, `r report(exp3a.results2, 2, 3, 2)`, excluding 1 influential participant). Nevertheless these two patterns of looking preference did not differ from each other,  a finding that differed from their preferences at test, `r report(exp3a.results3, 4, 3, 2)`. Thus, it is unclear whether infants' looking preferences at test reflect a true expectation that the agent would minimize danger. 

# Experiment 3: Minimizing risk (13-month-old infants)

```{r exp3b.primary}

exp3b.avg <- exp3.avg %>% filter(agegroup==13)

exp3b.info <- info(exp3b.avg)


exp3b.0 <- lmer(loglook ~ 1 + (1|subj),
               data = exp3b.avg)

exp3b.1 <- lmer(loglook ~ type + (1|subj),
               data = exp3b.avg)

# id influential observations
plot(influence(exp3b.1, "subj"), which="cook",
     cutoff=4/30, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation

exp3b.1.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp3b.avg %>% filter(subj != "24-MR"))
exp3b.1.table <- gen.m(exp3b.1.cooks)
exp3b.1.ci <- gen.ci(exp3b.1.cooks)[3:4,]

exp3b.1.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = exp3b.avg %>% filter(subj != "24-MR"))
exp3b.1.betas <- gen.beta(exp3b.1.beta)

exp3b.results <- cbind(exp3b.1.table, exp3b.1.betas, exp3b.1.ci)
```



```{r sim}
sim <- powerCurve(extend(exp3b.1, along="subj", n=500),
                       along="subj", breaks = c(24, 28, 32, 36, 40, 44, 48, 52), alpha = .05, seed = 123)
plot(sim)
print(sim)
```


```{r exp3b.pre}

exp3b.pre <- mr.pre %>% filter(agegroup == "13 months")

exp3b.2 <- lmer(loglook ~ type + (1|subj),
               data = exp3b.pre)

# id influential observations
plot(influence(exp3b.2, "subj"), which="cook",
     cutoff=4/30, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation

exp3b.2.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp3b.pre %>% filter(subj != "59-MR" & subj != "54-MR"))

exp3b.2.table <- gen.m(exp3b.2.cooks)
exp3b.2.ci <- gen.ci(exp3b.2.cooks)[3:4,]

exp3b.2.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = exp3b.pre %>% filter(subj != "59-MR" & subj != "54-MR"))
exp3b.2.betas <- gen.beta(exp3b.2.beta)

exp3b.results2 <- cbind(exp3b.2.table, exp3b.2.betas, exp3b.2.ci)
```

```{r exp3b.pre.vs.test}
exp3b.prefam.test <- long %>%
  filter(type == "Prefam High" | type == "Prefam Low" | type == "Higher" | type == "Lower") %>%
filter(experiment == "MR13") %>%
  mutate(phase = as.factor(case_when((type == "Prefam High" | type == "Prefam Low") ~ "prefam",
                           (type == "Higher" | type == "Lower") ~ "test"))) %>%
  mutate(cliff = as.factor(case_when((type == "Prefam High" | type == "Higher") ~ "deeper",
                                     (type == "Prefam Low" | type == "Lower") ~ "shallower")))

summary.mr <- summarySEwithin(data = exp3b.prefam.test, measurevar = "look", withinvars = c("cliff", "type", "phase"), idvar="subj")
  
exp3b.prefam.test$type <- as.factor(exp3b.prefam.test$type)

exp3b.3 <- lmer(loglook ~ cliff * phase + (1|subj),
                     data = exp3b.prefam.test)

plot(influence(exp3b.3, "subj"), which="cook",
     cutoff=4/30, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3b.3.table <- gen.m(exp3b.3)
exp3b.3.ci <- gen.ci(exp3b.3)[3:6,]

exp3b.3.beta <- lmer(scale(loglook) ~ cliff * phase + (1|subj),
                     data = exp3b.prefam.test)
exp3b.3.betas <- gen.beta(exp3b.3.beta)

exp3b.results3 <- cbind(exp3b.3.table,exp3b.3.betas,exp3b.3.ci)
```

### Main results.
Like 10-month-old infants in Experiment 1, 13-month-old infants looked longer at test when the agent, at test, chose the higher-risk action than when the agent chose the lower-risk action (Mhigher=`r summary.avg$look[5]`s, Mlower=`r summary.avg$look[6]`s, `r report(exp3b.results, 2, 3, 1)`, excluding one influential participant. This finding is consistent with an expectation that the agent would choose to perform the less perilous action. 

### Exploratory results.
Like in Experiment 1, we asked whether infants simply prefer to look at events occurring over the deeper cliff by comparing infants’ looking times at test to their looking times during control events, where their attention was drawn to each cliff. We found that overall, 13-month-old infants showed a preference for the shallower cliff in this context (Mdeep=`r summary.pre$look[3]`s, Mshallow=`r summary.pre$look[4]`s, `r report(exp3b.results2, 2, 3, 2)`, excluding 2 influential participants). In contrast to Experiment 1, these two patterns of looking preference significantly differed from each other `r report(exp3b.results3, 4, 3, 2)`. Thus, 13-month-old infants' expectations at test cannot be due to an intrinsic preference for events occurring over deeper to those over shallower cliffs. Instead, infants’ looking times at test reflect a reversal of their original preference for the shallow cliff, likely because they did not expect the agent to choose the more perilous action.

# Experiment 3: Combined analysis, Minimizing Risk (10 and 13-month-old infants)

```{r exp3.agediff}
exp3.0 <- lmer(loglook ~ type * agegroup + (1|subj),
               data = exp3.avg)
summary(exp3.0)

# id influential observations
plot(influence(exp3.0, "subj"), which="cook",
     cutoff=4/60, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3.0.cooks <- lmer(loglook ~ type * agegroup + (1|subj),
               data = exp3.avg %>% filter(subj != "03-MR"))
exp3.0.table <- gen.m(exp3.0.cooks)
exp3.0.ci <- gen.ci(exp3.0.cooks)[3:6,]

exp3.0.beta <- lmer(scale(loglook) ~ type * agegroup + (1|subj),
               data = exp3.avg %>% filter(subj != "03-MR"))
exp3.0.betas <- gen.beta(exp3.0.beta)

exp3.results <- cbind(exp3.0.table, exp3.0.betas, exp3.0.ci)
```


```{r exp3.together}
exp3.1 <- lmer(loglook ~ type + (1|subj),
               data = exp3.avg)
summary(exp3.1)

# id influential observations
plot(influence(exp3.1, "subj"), which="cook",
     cutoff=4/60, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3.1.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp3.avg %>% filter(subj != "03-MR"))
exp3.1.table <- gen.m(exp3.1.cooks)
exp3.1.ci <- gen.ci(exp3.1.cooks)[3:4,]

exp3.1.beta <- lmer(scale(loglook) ~ type+ (1|subj),
               data = exp3.avg %>% filter(subj != "03-MR"))
exp3.1.betas <- gen.beta(exp3.1.beta)

exp3.results0 <- cbind(exp3.1.table, exp3.1.betas, exp3.1.ci)

BF_exp3 <- exp((BIC(exp3.1.cooks) - BIC(exp3.0.cooks))/2) # go from BICS to Bayes Factors

BF_exp3 # extreme evidence for H0, which is that there's no difference between the age groups
```

```{r exp3.pre}
exp3.pre <- mr.pre 

exp3.2 <- lmer(loglook ~ type + (1|subj),
               data = exp3.pre)

# id influential observations
plot(influence(exp3.2, "subj"), which="cook",
     cutoff=4/60, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")
# one influential observation

exp3.2.cooks <- lmer(loglook ~ type + (1|subj),
               data = exp3.pre %>% filter(subj != "21-MR" & subj != "28-MR"))

exp3.2.table <- gen.m(exp3.2.cooks)
exp3.2.ci <- gen.ci(exp3.2.cooks)[3:4,]

exp3.2.beta <- lmer(scale(loglook) ~ type + (1|subj),
               data = exp3.pre %>% filter(subj != "21-MR" & subj != "28-MR"))
exp3.2.betas <- gen.beta(exp3.2.beta)

exp3.results2 <- cbind(exp3.2.table, exp3.2.betas, exp3.2.ci)
```

```{r exp3.pre.vs.test}
exp3.prefam.test <- long %>%
  filter(type == "Prefam High" | type == "Prefam Low" | type == "Higher" | type == "Lower") %>%
  filter(exp == "Exp.3" | exp=="Exp.1") %>%
  mutate(phase = as.factor(case_when((type == "Prefam High" | type == "Prefam Low") ~ "prefam",
                           (type == "Higher" | type == "Lower") ~ "test"))) %>%
  mutate(cliff = as.factor(case_when((type == "Prefam High" | type == "Higher") ~ "deeper",
                                     (type == "Prefam Low" | type == "Lower") ~ "shallower"))) %>%
    mutate(agegroup = as.factor(case_when(agem < 12 ~ "10 months",
                            agem > 12 ~ "13 months")))

summary.mr <- summarySEwithin(data = exp3.prefam.test, measurevar = "look", withinvars = c("cliff", "type", "phase"), idvar="subj")
  
exp3.prefam.test$type <- as.factor(exp3.prefam.test$type)

exp3.3 <- lmer(loglook ~ cliff * phase + (1|subj),
                     data = exp3.prefam.test)

plot(influence(exp3.3, "subj"), which="cook",
     cutoff=4/60, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3.3.table <- gen.m(exp3.3)
exp3.3.ci <- gen.ci(exp3.3)[3:6,]

exp3.3.beta <- lmer(scale(loglook) ~ cliff * phase + (1|subj),
                     data = exp3.prefam.test)
exp3.3.betas <- gen.beta(exp3.3.beta)

exp3.results3 <- cbind(exp3.3.table,exp3.3.betas,exp3.3.ci)
```

```{r exp3.pre.vs.test.agediff}

exp3.5 <- lmer(loglook ~ cliff * phase * agegroup + (1|subj), data = exp3.prefam.test)

plot(influence(exp3.5, "subj"), which="cook",
     cutoff=4/60, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3.5.table <- gen.m(exp3.5)
exp3.5.ci <- gen.ci(exp3.5)[3:10,]

exp3.5.beta <- lmer(scale(loglook) ~ cliff * phase * agegroup + (1|subj),
                     data = exp3.prefam.test)
exp3.5.betas <- gen.beta(exp3.5.beta)

exp3.results4 <- cbind(exp3.5.table,exp3.5.betas,exp3.5.ci)


BF_exp3.interaction <- exp((BIC(exp3.3) - BIC(exp3.5))/2) # go from BICS to Bayes Factors

BF_exp3.interaction # extreme evidence for H0, which is that there's no difference between the age groups
```


```{r exp3.diffpre}
exp3.4 <- lmer(loglook ~ type * agegroup + (1|subj),
               data = exp3.pre)
summary(exp3.4)

# id influential observations
plot(influence(exp3.4, "subj"), which="cook",
     cutoff=4/60, sort=TRUE,
     xlab="Cook´s Distance",
     ylab="Subject ID")

exp3.4.cooks <- lmer(loglook ~ type * agegroup + (1|subj),
               data = exp3.pre %>% filter(subj != "21-MR" & subj != "28-MR"))
exp3.4.table <- gen.m(exp3.4.cooks)
exp3.4.ci <- gen.ci(exp3.4.cooks)[3:6,]

exp3.4.beta <- lmer(scale(loglook) ~ type * agegroup + (1|subj),
               data = exp3.pre %>% filter(subj != "21-MR" & subj != "28-MR"))
exp3.4.betas <- gen.beta(exp3.4.beta)

exp3.results4 <- cbind(exp3.4.table, exp3.4.betas, exp3.4.ci)


BF_exp3.pre <- exp((BIC(exp3.2.cooks) - BIC(exp3.4.cooks))/2) # go from BICS to Bayes Factors

BF_exp3.pre # extreme evidence for H0, which is that there's no difference between the age groups
```


### Results Across Age Groups
Across both age groups, infants looked longer at test when the agent, at test, chose the higher-risk action than when the agent chose the lower-risk action (Mhigher=`r summary.1013$look[3]`s, Mlower=`r summary.1013$look[4]`s, `r report(exp3.results0, 2, 3, 1)`, excluding one influential participant). And across both age groups, infants’ looking preferences for the cliffs during control events differed from their looking preferences at test, xxxx.

### Comparing to Control Videos
Further analyses tested for an alternative explanation for this looking preference: Did infants simply prefer to look at events occurring over the deeper cliff? To address this possibility, we compared infants’ looking times during control events, where their attention was drawn to each cliff, using an attention-getting star that was placed in the path of the agent’s subsequent actions. We found that overall, infants showed a preference for the shallower cliff in this context (Mdeep=`r summary.pre.1013$look[1]`s, Mshallow=`r summary.pre.1013$look[2]`s, `r report(exp3.results2,2,3,2)`.  Infants’ looking preferences between the control events and the test events significantly differed from each other (`r report(exp3.results3,3,3,2)`).

### Comparing 10 and 13mo infants
The two groups of infants did not differ in looking time during test events (`r report(exp3.results,4,3,2)`). The two groups of infants also did not differ in looking time during control events (`r report(exp3.results4,4,3,2)`).


# Supplemental Analyses

```{r log, include = TRUE}
# is a lognormal transformation justified given the distribution of looks?
fig.S1 <- ggplot(data = risk.avg, aes(look, fill=exp))
fig.S1 +
  geom_density(alpha = 0.5)+
  # geom_text(aes(experiment))+
  theme_linedraw(15)+
  xlab("Looking Time (s)")+
  scale_fill_brewer(palette="Set2")

normal.ll <- fitdistr(risk.avg$look, "normal")$loglik
lognormal.ll <- fitdistr(risk.avg$look, "lognormal")$loglik
```

**Figure S1.** Density plot of looking times during test for Experiments 1 and 2 (total N=`r length(unique(risk.avg$subj))`). Maximum-likelihood fitting revealed that the lognormal distribution (log likelihood=`r lognormal.ll`) provides a better fit to these data than the normal distribution (log likelihood=`r normal.ll`).

## Power analysis over experiment 1
```{r exp1.power}
sim <- powerCurve(extend(exp1.1, along="subj", n=500),
                       along="subj", breaks = c(36, 40, 44, 48, 52, 56, 60, 64, 68), alpha = .05, seed = 123)
plot(sim)
print(sim)

```

